**Weighted mean** : $\quad\quad\overline{X}=\dfrac{\sum_{i=1}^n w_i X_i}{\sum_{i=1}^n w_i}$

- **Geometric mean** : $\quad\quad\overline{X}=\left(\prod_{i=1}^n X_i\right)^{\frac{1}{n}}$

- **Harmonic mean** : $\quad\quad\overline{X}=\frac{n}{\sum_{i=1}^n \frac{1}{X_i}}$





### Boxplots



## 

### Univariate statistics

Going back with the dataset `iris`

```{r}
#| echo: true
data(iris)
```

To get a global view

```{r}
#| echo: true
summary(iris)
```

## 

### Graphic Representations

```{r}
#| echo: true
boxplot(iris$Sepal.Length, col = c("yellow"),main = "Boxplot", ylab = "Quantiles")
```

## 

```{r}
#| echo: true
boxplot(iris[,c('Sepal.Length','Sepal.Width','Petal.Length','Petal.Width')],
  col = c("yellow"),
  main = paste("Boxplot"),
  ylab = "Quantiles")
```

## 

```{r}
#| echo: true
hist(iris$Sepal.Length,
  col = c("orange"),
  main = paste("Histogram for the (quantitative) variable Sepal.Length"),
  ylab = "Frenquency",
  xlab = "Sepal Length")
```

## 

Now let's look the qualitative variable `Species`

```{r}
#| echo: true
table_Species <- table(iris$Species)
table_Species
```

```{r}
#| echo: true
prop.table(table_Species)
```

```{r}
#| echo: true
barplot(table_Species, col="orange")
```

### Bivariate statistics

coming.

# Part 2 - Probability

## Chapter 1 - Randomnes

### Random experiment

An experiment is called **random** if

-   it can be **repeated**
-   it has **several** possible outcomes
-   whose outcome is **unpredictable**

Examples:

-   rolling a six-sided die
-   observing the disease status of a plant

## 

### Elementary Event

An **elementary event** is a result of a random experiment.

Examples:

-   Getting a 3 when rolling a 6-sided die
-   Observing a plant being sick

### Sample Space

The **Sample space** (denoted by $\Omega$) is the set of **all possible outcomes** (elementary events) of a random experiment.

Example :

-   Rolling a 6-sided die, $\Omega = \left\{1, 2, 3, 4, 5, 6 \right\}$

## 

### Property of a Sample Space

A Sample Space $\Omega$ can be :

-   a **finite** set
-   a **countably** infinite set
-   an **uncountably** infinite set

Note :

-   $\Omega$ is **discrete** : finite or countably infinite
-   $\Omega$ is **continuous** : uncountably infinite

## 

### Event (Non-Elementary)

A (Non-Elementary) Event is subset of $\Omega$.

Example :

$\to$ Event A : “Getting a result strictly greater than 4 when rolling a 6-sided die”

$\to$ A=$\{5,6\}$

#### Particular events

-   The event $\Omega$ is certain
-   The empty set $\emptyset$ is an impossible event

# Part 3 - Estimation and Confidence Intervals


